Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-08 main.tex
First version of abstract

\begin{abstract}
    TDB
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A different paradigm for educative robots}

@@

\subsubsection{Context, Study Design}
It was the first time we where trying a long-terme interaction between a child
and the CoWriter robot. So the first aim of this study was to see if such an
interaction was simply possible. If we could create an environement to keep a child engaged
during one hour just in writing words with the robot.
The second question was focused on the content of the interaction. Our goal was
to figure out what extent the child would actually improve the robot's
writing.\\

Diego is a six years old child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplifiyed by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

The experiment took one month. It was divided in four sessions of one hour, one session per week.
In order to justify to the child an activity where a robot wants to learn
handwriting, we decided to adduce a scenario. There where two Nao robots: a
blue one (Mimi) and an orange one (Clem). They where introduced to the child as
two hold friends. Mimi was left, and the two robots were corresponding by
handwrited mails. But Clem was begining in writing and it needed the help of
Diego to write its responses to Mimi.\\

During the first session, Diego was just teaching single letters to the robot.
progressively we increased the difficulty : the second session he was teaching
shirt words and in third session he was teaching long sentences. The last session was more like a test for Clem
: it had to prove to Mimi that it actually improved its handwriting thanks to
Diego.

@@

\subsubsection{Results}
Diego completly accepted our scenario and seriously played the game. At the
begining he seemed not confident and intimidated.  But quickly, he gain in
confidence and complicity with the robot. Finally, he showed a real affinity, so
that he sent an handwrited mail to it some days after the last
session.\\

In all sessions, Diego was fully focused on the activity during forty minutes up to one
hour. In total, he provided X letters as demonstration.\\

Diego felt he improved the robot's handwriting. To make clearly visible this
improvement, we printed the letter that the robot writted during the third
session before and after the help of diego~\ref{fig:stimuli}.

@@

\subsubsection{Context, Study Design}
Henry is a five and half years old child. It is followed by an occupational
therapist. According to the therapist, he presents visuo-constructive deficits.
From our perspective, the main effect of this trouble during handwriting
activity was that Henry
did not have any mental template to draw the shape of a letter. So he was 
apparently performing random attempts and then was comparing with the provided template.
What is more, Henry is strongly careless : he rarely payed attention to
advices, even to what he was doing when he was currently drawing, and he was
quickly shifting his attention from one
activity to another.
Hence, the goal of this study is to face those two chalenging issues
(visuo-constructive deficits and inattention) in order to keep Henry focused
on the activity during forty-minutes interactions, and to make the robot
evidently learning from his demonstrations.\\

This experiment took place in the therapist's office. It was divided in four
sessions as well. This time, we assumed that a complex cenario like the one for Diego was
no longer relevent with Henry. We just introduced the robot and quickly
said that it was seeking help to train for a robot handwriting contest.\\

@@

Since Henry was frequently drawing horizontaly inverted numbers, or even
absolutly unrecognizable shapes, we programmed the robot to refuse shapes that
was too distant to a reference with a threshold we arbitrary fixed. In that way,
the child was forced to take care on what he was providing to the robot as
demonstration. Also, to make sure the robot was going to improve its handwriting
and to clearly show this improvement, we decided to make it completly starting
from scratch : for all numbers, the first try of the robot resulted in
a simple vertical stroke (see the first robot's try in~\ref{learning_6_demos}).

@@

\subsubsection{Results}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_demos}
    \caption{\small Henry's demonstrations for the number ``6'' (top row) and
        corresponding shapes generated by the robot. After eight demomstrations,
        Henry decided that the robot's ``6'' was good enough, and went to
    another character: in that respect, he was the one leading the learning
process of the robot.}
    \label{learning_6_demos}
\end{figure}

>>>>

\begin{abstract}

    Robots for education are not limited to support ICT teaching, and robots are
    finding new ways to enter and blend in the classroom. This article reports
    on such a new paradigm for educative robots, that involves \emph{learning by
    teaching} and strong \emph{social engagement} to help children struggling
    with handwriting. Our system relies on machine-learning and child-robot
    interaction with a small humanoid robot, and we present several real-world
    studies in schools and with occupational therapists that led us to promising
    initial results.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Different Paradigm for Educative Robots}

@@

\subsubsection{Context, Study Design}
It was the first time we where trying a long-term interaction between a child
and the CoWriter robot. So the first aim of this study was to see if such an
interaction was simply possible. If we could create an environment to keep a child engaged
during one hour just in writing words with the robot.
The second question was focused on the content of the interaction. Our goal was
to figure out what extent the child would actually improve the robot's
writing.\\

Diego is a six years old child. 
Before the experiment, we could create a dataset of letters based on his main
mistakes, but amplified by PCA. Our idea was to make the robot
exaggerating the mistakes of Diego. Thus, by correcting the robot, 
Diego was actually going to correct himself.\\

The experiment took one month. It was divided in four sessions of one hour, one session per week.
In order to justify to the child an activity where a robot wants to learn
handwriting, we decided to adduce a scenario. There where two Nao robots: a
blue one (Mimi) and an orange one (Clem). They where introduced to the child as
two hold friends. Mimi was left, and the two robots were corresponding by
handwritten mails. But Clem was beginning in writing and it needed the help of
Diego to write its responses to Mimi.\\

During the first session, Diego was just teaching single letters to the robot.
Gradually we increased the difficulty : the second session he was teaching
shirt words and in third session he was teaching long sentences. The last session was more like a test for Clem
: it had to prove to Mimi that it actually improved its handwriting thanks to
Diego.

@@

\subsubsection{Results}
Diego completely accepted our scenario and seriously played the game. At the
beginning he seemed not confident and intimidated.  But quickly, he gain in
confidence and complicity with the robot. Finally, he showed a real affinity, so
that he sent an handwritten mail to it some days after the last
session.\\

In all sessions, Diego was fully focused on the activity during forty minutes up to one
hour. In total, he provided 154 letters as demonstration.\\

Diego felt he improved the robot's handwriting. To make clearly visible this
improvement, we printed the letter that the robot wrote during the third
session before and after the help of Diego~\ref{fig:stimuli}.

@@

\subsubsection{Context, Study Design}
Henry is a five and half years old child. It is followed by an occupational
therapist. According to the therapist, he presents visuo-constructive deficits.
From our perspective, the main effect of this trouble during handwriting
activity was that Henry
did not have any mental template to draw the shape of a letter. So he was 
apparently performing random attempts and then was comparing with the provided template.
What is more, Henry is strongly careless : he rarely payed attention to
advices, even to what he was doing when he was currently drawing, and he was
quickly shifting his attention from one
activity to another.
Hence, the goal of this study is to face those two challenging issues
(visuo-constructive deficits and inattention) in order to keep Henry focused
on the activity during forty-minutes interactions, and to make the robot
evidently learning from his demonstrations.\\

This experiment took place in the therapist's office. It was divided in four
sessions as well. This time, we assumed that a complex scenario like the one for Diego was
no longer relevant with Henry. We just introduced the robot and quickly
said that it was seeking help to train for a robot handwriting contest.\\

@@

Since Henry was frequently drawing horizontally inverted numbers, or even
absolutely unrecognizable shapes, we programmed the robot to refuse shapes that
was too distant to a reference with a threshold we arbitrary fixed. In that way,
the child was forced to take care on what he was providing to the robot as
demonstration. Also, to make sure the robot was going to improve its handwriting
and to clearly show this improvement, we decided to make it absolutely starting
from scratch : for all numbers, the first try of the robot resulted in
a simple vertical stroke (see the first robot's try in~\ref{learning_6_demos}).

@@

\subsubsection{Results}
Despite his inattention, Henry was able to keep on the activity during more than
forty minutes in each session.\\

As soon as Henry understood that the robot was only accepting recognizable
shapes, he started to take care on the shapes he was providing to it. He used the
clearing button to retry when he judged that his numbers where not going to be
accepted by the robot. According to the therapist, it was the first time Henry
was intrinsically correcting himself.\\

Since the robot was learning from scratch, each time Henry succeeded to make his
demonstrations accepted by it, the improvement of its handwriting was
obvious~\ref{learning_6_demos},~\ref{henry_distances}.
Therefor, Henry quickly enter in an self-rewarding game where the rewards were
the improvement of the robot. In total, over the three last sessions he provided 99
demonstrations of number shapes to the robot.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{learning_6_demos}
    \caption{\small Henry's demonstrations for the number ``6'' (top row) and
        corresponding shapes generated by the robot. After eight demonstrations,
        Henry decided that the robot's ``6'' was good enough, and went to
    another character: in that respect, he was the one leading the learning
process of the robot.}
    \label{learning_6_demos}
\end{figure}
